---
title: "DateMap_HW_Freddie_Ben"
author: "Frederick Cain"
date: "2025-02-24"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(lubridate)
library(dplyr)
library(purrr)
```
# 1) Generate a sequence of dates from January 1, 2015 to December 31, 2025, spaced by every two months. Extract the year, quarter, and ISO week number for each date.
```{r}
# Generate sequence of dates every two months
dates_seq <- seq(ymd("2015-01-01"), ymd("2025-12-31"), by = "2 months")

# Extract Year, Quarter, and ISO week
dates_df <- tibble(
  date = dates_seq,
  year = year(dates_seq),
  quarter = quarter(dates_seq),
  iso_week = isoweek(dates_seq)
)

# Print output
print(dates_df)

```
# 2) Given the following dates, compute the difference in months and weeks between each con- secutive pair.
sample_dates <- c("2018-03-15", "2020-07-20", "2023-01-10", "2025-09-05")
```{r}
# Define the date vector
sample_dates <- ymd(c("2018-03-15", "2020-07-20", "2023-01-10", "2025-09-05"))

# Compute differences in months and weeks
date_diffs <- tibble(
  start_date = head(sample_dates, -1),
  end_date = tail(sample_dates, -1),
  months_diff = as.numeric(interval(start_date, end_date) / months(1)),
  weeks_diff = as.numeric(interval(start_date, end_date) / weeks(1))
)

# Print output
print(date_diffs)

```
# 3) Using map() and map_dbl(), compute the mean, median, and standard deviation for each numeric vector in the following list:
num_lists <- list(c(4, 16, 25, 36, 49), c(2.3, 5.7, 8.1, 11.4), c(10, 20, 30, 40, 50))

```{r}
# Define the list of numeric vectors
num_lists <- list(c(4, 16, 25, 36, 49), c(2.3, 5.7, 8.1, 11.4), c(10, 20, 30, 40, 50))

# Compute mean, median, and standard deviation
stats_df <- tibble(
  mean = map_dbl(num_lists, mean),
  median = map_dbl(num_lists, median),
  sd = map_dbl(num_lists, sd)
)

# Print output
print(stats_df)

```
# 4) Given a list of mixed date formats, use map() and possibly() from purrr to safely convert them to Date format and extract the month name.
date_strings <- list("2023-06-10", "2022/12/25", "15-Aug-2021", "InvalidDate")
```{r}
# Define the list of mixed date formats
date_strings <- list("2023-06-10", "2022/12/25", "15-Aug-2021", "InvalidDate")

# Safe date parsing using possibly()
safe_parse_date <- possibly(ymd, otherwise = NA)

# Convert dates and extract month names
converted_dates <- map(date_strings, safe_parse_date)
month_names <- map_chr(converted_dates, ~ ifelse(!is.na(.), month(. , label = TRUE), "Invalid"))

# Store results in tibble
date_results <- tibble(
  original = date_strings,
  parsed_date = converted_dates,
  month_name = month_names
)

# Print output
print(date_results)

```
