---
title: "dottable_hw"
output: html_document
date: "2025-03-04"
---

```{r}
library(tidyverse)
library(dplyr)
library(data.table)
```

1) Use and show data.table code to select the variables year, month, day, and hour from the imported flights data
```{r}
nycdata <- fread("nycdata.csv") 

#use your own local folder. I was having issues with relative paths 

filter1 <- nycdata[, .(year, month, day, hour)]

filter1
```

2) Use and show data. table code to produce a table that shows a carrier of DL, an origin of JFK and a destination of SEA

```{r}
filter2<- nycdata[carrier == "DL" & origin == "JFK" & dest == "SEA"]

filter2
```

3) Use and show data.table code to produce a table that shows a carrier of UA, a month of March, and an airtime that is below 330.

```{r}
filter3 <- nycdata[carrier == "UA" & month == 3 & air_time < 330]

filter3
```

4) Use and show tidyverse code to produce a table that shows a carrier of UA, a month of March, and an airtime that is below 330.

```{r}
nycdata %>%
  filter(carrier == "UA", month == 3, air_time < 330) ->filter3

filter3
```

5) Use the data.table method to add a variable called speed that is the average air speed of the plane in miles per hour.
```{r}
nycdata[, speed := (distance * 60) / air_time]

# Check if the new column is added
head(nycdata[, .(carrier, origin, dest, air_time, distance, speed)])

```

6) Use the tidyverse method to add a variable called speed that is the average air speed of the plane in miles per hour.
```{r}
nycdata <- nycdata %>%
  mutate(speed = distance / (air_time / 60)) # Speed = distance / time in hours

# Show the first few rows
head(nycdata)

```

7) Show and use coding to change the carrier abbreviation of UA to UniitedAir,
7a. data.table method
7b. tidyverse method (Use a sequence of dplyr commands so that you can see the change in your table)
```{r}

```

