---
title: "dottable_hw"
output: html_document
date: "2025-03-04"
---

```{r}
library(tidyverse)
library(dplyr)
library(data.table)
```

1) Use and show data.table code to select the variables year, month, day, and hour from the imported flights data
```{r}
nycdata <- fread("nycdata.csv") 

#use your own local folder. I was having issues with relative paths 

filter1 <- nycdata[, .(year, month, day, hour)]

filter1
```

2) Use and show data. table code to produce a table that shows a carrier of DL, an origin of JFK and a destination of SEA

```{r}
filter2<- nycdata[carrier == "DL" & origin == "JFK" & dest == "SEA"]

filter2
```

3) Use and show data.table code to produce a table that shows a carrier of UA, a month of March, and an airtime that is below 330.

```{r}
filter3 <- nycdata[carrier == "UA" & month == 3 & air_time < 330]

filter3
```

4) Use and show tidyverse code to produce a table that shows a carrier of UA, a month of March, and an airtime that is below 330.

```{r}
nycdata %>%
  filter(carrier == "UA", month == 3, air_time < 330) ->filter3

filter3
```

