---
title: "dottable_hw"
output: html_document
date: "2025-03-04"
---

```{r}
library(tidyverse)
library(dplyr)
library(data.table)
```

1) Use and show data.table code to select the variables year, month, day, and hour from the imported flights data
```{r}
nycdata <- fread("C:/Users/btaus/nycdata.csv") 
#use your own local folder. I was having issues with relative paths

filter1 <- nycdata[, .(year, month, day, hour)]

filter1
```

2) Use and show data. table code to produce a table that shows a carrier of DL, an origin of JFK and a destination of SEA

```{r}
filter2<- nycdata[carrier == "DL" & origin == "JFK" & dest == "SEA"]

filter2
```

3) Use and show data.table code to produce a table that shows a carrier of UA, a month of March, and an airtime that is below 330.

```{r}
filter3 <- nycdata[carrier == "UA" & month == 3 & air_time < 330]

filter3
```

4) Use and show tidyverse code to produce a table that shows a carrier of UA, a month of March, and an airtime that is below 330.

```{r}
nycdata %>%
  filter(carrier == "UA", month == 3, air_time < 330) ->filter3

filter3
```

Use the data.table method to add a variable called speed that is the average air speed of the plane in miles per hour.

Use the tidyverse method to add a variable called speed that is the average air speed of the plane in miles per hour.

Show and use coding to change the carrier abbreviation of UA to UniitedAir,
    7a. data.table method
    7b. tidyverse method (Use a sequence of dplyr commands so that you can see the change in your table)



